\begin{thebibliography}{99}
\bibitem{liu2015deep}
  F.~Liu, C.~Shen, and G.~Lin, ``Deep convolutional neural fields for depth
  estimation from a single image,'' in \emph{Proceedings of the IEEE Conference
    on Computer Vision and Pattern Recognition}, 2015, pp. 5162--5170.

\bibitem{eigen2014depth}
  D.~Eigen, C.~Puhrsch, and R.~Fergus, ``Depth map prediction from a single image
  using a multi-scale deep network,'' in \emph{Advances in neural information
    processing systems}, 2014, pp. 2366--2374.

\bibitem{laina2016deeper}
  I.~Laina, C.~Rupprecht \emph{et~al.}, ``Deeper depth prediction with fully
  convolutional residual networks,'' in \emph{3D Vision (3DV), 2016 Fourth
    International Conference on}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE,
  2016, pp. 239--248.

\bibitem{Geiger2012CVPR}
  A.~Geiger, P.~Lenz, and R.~Urtasun, ``Are we ready for autonomous driving? the
  kitti vision benchmark suite,'' in \emph{Conference on Computer Vision and
    Pattern Recognition (CVPR)}, 2012.

\bibitem{kuznietsov2017semi}
  Y.~Kuznietsov, J.~St{\"u}ckler, and B.~Leibe, ``Semi-supervised deep learning
  for monocular depth map prediction,'' \emph{arXiv preprint arXiv:1702.02706},
  2017.

\bibitem{godard2016unsupervised}
  C.~Godard, O.~Mac~Aodha, and G.~J. Brostow, ``Unsupervised monocular depth
  estimation with left-right consistency,'' \emph{arXiv preprint
    arXiv:1609.03677}, 2016.


\bibitem{hawe2011dense}
  S.~Hawe, M.~Kleinsteuber, and K.~Diepold, ``Dense disparity maps from sparse
  disparity measurements,'' in \emph{Computer Vision (ICCV), 2011 IEEE
    International Conference on}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE,
  2011, pp. 2126--2133.

\bibitem{liu2015depth}
  L.-K. Liu, S.~H. Chan, and T.~Q. Nguyen, ``Depth reconstruction from sparse
  samples: Representation, algorithm, and sampling,'' \emph{IEEE Transactions
    on Image Processing}, vol.~24, no.~6, pp. 1983--1996, 2015.

\bibitem{ma2016sparse}
  F.~Ma, L.~Carlone \emph{et~al.}, ``Sparse sensing for resource-constrained
  depth reconstruction,'' in \emph{Intelligent Robots and Systems (IROS), 2016
    IEEE/RSJ International Conference on}.\hskip 1em plus 0.5em minus 0.4em\relax
  IEEE, 2016, pp. 96--103.

\bibitem{sparsetodense}
  F.Ma, S. Karaman, ``Sparse-to-Dense: Depth Prediction from Sparse Depth Samples and a Single Image'', \emph{arXiv preprint arXiv:1709.07492}, 2017
  
\bibitem{elad}
  M. Elad. \emph{Sparse and Redundant Representations}. New York, NY: Springer, 2010

\bibitem{papyan}
  Vardan, Papyan \& Romano, Yaniv \& Elad, Michael. ``Convolutional Neural Networks Analyzed via Convolutional Sparse Coding''. \emph{Journal of Machine Learning Research}. 18. 2016

\bibitem{murdock}
  Mudock.... need that manuscript up....

\bibitem{uhrig}
  J. Uhrig, N. Schneider, L. Schneider, U. Franke, A. Geiger. ``Sparsity Invariant CNNs'', \emph{arXiv preprint arXiv:1708.06500}, 2017

\bibitem{sulam}
  J. Sulam, V. Papyan, Y. Romano, M. Elad. ``Multi-Layer Convolutional Sparse Modeling: Pursuit and Dictionary Learning''. \emph{arXiv preprint arXiv:1708.08705}

\bibitem{riegler}
  G. Riegler, M. Ruther, H. Bischof. ``ATGV-Net: Accurate Depth Super-Resolution.''. in \emph{European Conference on Computer Vision}, 2016

\bibitem{Jampani2016CVPR}
  V.~Jampani, M.~Kiefel, and P.~V. Gehler.
  \newblock Learning sparse high dimensional filters: Image filtering, dense crfs
  and bilateral neural networks.
  \newblock In {\em Proc. IEEE Conf. on Computer Vision and Pattern Recognition
    (CVPR)}, 2016.
\bibitem{schneider2016semantically}
  N.~Schneider, L.~Schneider, P.~Pinggera, U.~Franke, M.~Pollefeys, and
  C.~Stiller.
  \newblock Semantically guided depth upsampling.
  \newblock In {\em Proc. of the German Conference on Pattern Recognition
    (GCPR)}, pages 37--48. Springer, 2016.

\bibitem{barron2016fast}
J.~T. Barron and B.~Poole.
\newblock The fast bilateral solver.
\newblock In {\em Proc. of the European Conf. on Computer Vision (ECCV)}, pages
  617--632. Springer, 2016.

\bibitem{Ferstl2013}
D.~Ferstl, C.~Reinbacher, R.~Ranftl, M.~Ruether, and H.~Bischof.
\newblock {Image Guided Depth Upsampling Using Anisotropic Total Generalized
  Variation}.
\newblock In {\em Proc. of the IEEE International Conf. on Computer Vision
  (ICCV)}, 2013.

\bibitem{Nadaraya}
E.~Nadaraya.
\newblock On estimating regression.
\newblock In {\em Theory of Probability and its Applications}, 1964.

\bibitem{Watson}
G.~Watson.
\newblock Smooth regression analysis.
\newblock In {\em Sankhyā: The Indian Journal of Statistics}, 1964.

\end{thebibliography}